% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[kevin-caye]{Kevin Caye}

\thinrule

\startblockquote
Computer Science - Statistics - Machine Learning Optimization - Data
Visualization - Operational Research
\stopblockquote

\thinrule

\subsection[skills]{skills}

\startdescription{Computer science}
  {\bf Programming :} R, python, C/C++, scala (beginner).

  {\bf OS :} Linux, OS X

  {\bf Tools :} Emacs, Org-mode, Git, Rstudio, Jupyter, Docker.
\stopdescription

\startdescription{Mathematics}
  Optimization, Statistics, Probabilistic modeling, Machine learning,
  Operational Research.
\stopdescription

\startdescription{Languages}
  {\bf English :} good working knowledge

  {\bf Spanish :} basic communication skills
\stopdescription

\subsection[education]{Education}

\startdescription{2014-oct. 2017}
  {\bf Applied mathematics phd}; TIMC-IMAG, La Tronche (38) and
  Gipsa-lab, Saint Martin D'hères (38)

  {\em Matrix factorization methods for population genomics and
  association mapping}
\stopdescription

\startdescription{2011-2014}
  {\bf Engineer in computer science and applied mathematics};
  Grenoble-INP, ENSIMAG, Saint-Martin D'Heres (38)

  {\em Major : MMIS (Mathematical Modeling, simulation and Image)}
\stopdescription

\startdescription{2008-2011}
  {\bf Classe préparatoire MPSI/MP*}; lycée Albert schweitzer, Le Raincy
  (93)
\stopdescription

\subsection[professional-experience]{Professional Experience}

\startdescription{2017-nov. Today}
  {\bf Service Provider.}; Kaizen Solutions, Meylan (38). I am currently
  working within the research and development team \quotation{Analytics
  Applications and Programs} of Schneider Electric. This team is in
  charge of developing algorithms and programs for data analysis (energy
  consumption of buildings, detection of faults on electrical equipment,
  etc.).
\stopdescription

\startdescription{2014-oct. 2017}
  {\bf Applied mathematics phd.} Ways to represent health and the living
  have changed considerably in recent years. The news representations
  are based on massive data collection coming from high throughput
  sequencing technologies. The objective of this thesis was to develop
  methods to detect associations between variables in such biological
  data. More especially, we were interested in statistical modeling
  based on optimization problems based on matrix factorizations.
\stopdescription

\startdescription{2014-2016}
  {\bf Teaching.}

  \startitemize[packed]
  \item
    Mathematics beginner courses for L1 students at UGA
  \item
    Mathematics support courses for L1 student at UGA
  \item
    Population dynamics courses for L1 student at UGA
  \item
    End of year data science project for M1 student at l'ENSIMAG
  \stopitemize
\stopdescription

\startdescription{Février-Août 2014}
  {\bf Research and development internship}; Dassault Systèmes,
  Vélizy-Villacoublay (78).

  In the Science and Corporate Research* team, I made a scientific
  literature review of the 3D simulation methods based on examples. Then
  I implemented a prototype using OpenGL and C++.
\stopdescription

\startdescription{Juillet-Août 2013}
  {\bf Research and development internship}; INRIA, Montbonnot (38). In
  the MAVERICK team, I implemented 3D rendering method for the voxel
  based rendering pipeline called Gigavoxel (C++, GLSL, CUDA).
\stopdescription

\subsection[scientific-publications]{Scientific Publications}

{\bf Fast Inference of Individual Admixture Coefficients Using
Geographic Data}\crlf
Kevin Caye, Flora Jay, Olivier Michel, Olivier François\crlf
{\em The Annals of Applied Statistics}

{\bf Identifying outlier loci in admixed and in continuous populations
using ancestral population differentiation statistics}\crlf
Helena Martins, Kevin Caye, Keurcien Luu, Michael GB Blum, Olivier
François\crlf
{\em bioRxiv}; doi:
\useURL[url1][http://dx.doi.org/10.1101/054585][][10.1101/054585]\from[url1]

{\bf TESS3: fast inference of spatial population structure and genome
scans for selection}\crlf
Kevin Caye, Timo M. Deist, Helena Martins, Olivier François\crlf
{\em Molecular ecology resources}, 2016, vol.~16, no 2, p.~540-548; doi:
\useURL[url2][http://dx.doi.org/10.1111/1755-0998.12471][][10.1111/1755-0998.12471]\from[url2]

\subsection[interests]{Interests}

\startdescription{Sports}
  Kyokushin karate, multisport raid and other mountain sports (skying,
  trekking)
\stopdescription

\startdescription{Applied Mathematics}
  data science and applied mathematics web competitions
\stopdescription

\thinrule

\startblockquote
\useURL[url3][mailto:kevin.caye@gmail.com][][kevin.caye@gmail.com]\from[url3]
• +33 6 19 45 11 46 • 28 ans\crlf
1 rue du tenaison - Saint-Egrève 38120, France\crlf
\useURL[url4][https://cayek.github.io/]\from[url4]
\stopblockquote

\stoptext
